Mega-analysis of the Interoceptive Accuracy Scale (IAS)

### 2025-10-21 analysis/Study1.qmd
BFI updated df9

```{r}
df9 <- read.csv("../data/VonMohr2023/DataSet_study3.csv")
df9 <- df9[complete.cases(select(df9, starts_with("IAS_"))), ]
df9 <- df9 |>
  mutate(Gender = as.character(ifelse(GENDER == "Man", "Male", ifelse(GENDER == "Woman", "Female", "Other")))) |>
  rename(
    Age=AGE, Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  ) |>
  mutate(across(starts_with("BFI_"), \(x) datawizard::rescale(x, to = c(0, 1)))) |>
  mutate(
    Neuroticism = (BFI_1 + BFI_2 + BFI_3)/3,
    Agreeableness = (BFI_10R + BFI_11 + BFI_12)/3,
    Extraversion = (BFI_4 + BFI_5 + BFI_6)/3,
    Conscientiousness = (BFI_13 + BFI_14 + BFI_15R)/3,
    Openness = (BFI_7 + BFI_8 + BFI_9)/3)

>>>>

```{r}
df9 <- read.csv("../data/VonMohr2023/DataSet_study3.csv")
df9 <- df9[complete.cases(select(df9, starts_with("IAS_"))), ]
df9 <- df9 |>
  mutate(Gender = as.character(ifelse(GENDER == "Man", "Male", ifelse(GENDER == "Woman", "Female", "Other")))) |>
  rename(
    Age=AGE, Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  ) |>
  mutate(across(starts_with("BFI_"), \(x) datawizard::rescale(x, to = c(0, 1)))) |>
  mutate(
    Neuroticism = (BFI_5 + BFI_10 + BFI_15)/3,
    Agreeableness = (BFI_3 + BFI_6 + BFI_13)/3,
    Extraversion = (BFI_2 + BFI_8 + BFI_12)/3,
    Conscientiousness = (BFI_1 + BFI_7 + BFI_11)/3,
    Openness = (BFI_4 + BFI_9 + BFI_14)/3)
